\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{ragged2e}

% Font (you can switch to Times or another serif font if Georgia isn't available)
\setmainfont{Georgia}

% No section numbers
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

% Centered Name
\begin{center}
    {\LARGE \textbf{Moffat Kagiri Ngugi}}\\[0.5em]
    0740-294-373 \quad | \quad \href{mailto:kagirimoffat@outlook.com}{kagirimoffat@outlook.com} \quad | \quad
    \href{https://www.linkedin.com/in/moffatkagiri/}{LinkedIn} \quad | \quad
    \href{https://github.com/moffat-kagiri}{GitHub}
\end{center}

\section*{Education}
\justifying
\textbf{University of East London} — London, UK \\
\textit{Master of Science in Data Science} \hfill Mar. 2022 – Present

\textbf{Daystar University} — Nairobi, KE \\
\textit{Bachelor of Science in Actuarial Science} \hfill Aug. 2017 – Nov. 2021

\section*{Experience}
\textbf{Liberty \& Heritage Insurance} — Nairobi, KE \\
\textit{Actuarial Graduate Trainee} \hfill Apr 2025 – Present
\begin{itemize}[leftmargin=*]
    \item Developed interactive dashboards (Power BI, Excel) for business acquisition tracking, improving decision-making across sales and underwriting teams.
    \item Conducted data-driven policy analysis and automated renewal workflows using actuarial principles and claims experience metrics.
    \item Applied statistical insights and loss ratio analysis to support underwriting decisions and pricing strategy.
    \item Collaborated with cross-functional teams to integrate actuarial feedback into product design, marketing, and distribution strategy.
    \item Contributed to public-sector tender preparation through technical documentation, compliance analysis, and stakeholder engagement.
\end{itemize}

\textbf{Gauss Analytics} — Nairobi, KE \\
\textit{Founder \& Lead Data Scientist} \hfill Jan 2025 – Present
\begin{itemize}[leftmargin=*]
    \item Founded a data analytics and financial insight firm serving SMEs, NGOs, and professional service firms.
    \item Designed and implemented tiered analytics solutions: Foundational Analytics, Advanced Analytics \& Architecture, and Embedded DSaaS.
    \item Built custom data pipelines, automated reporting systems, and interactive dashboards to improve decision speed and financial visibility.
    \item Developed \textbf{Fedha}, an SME-focused financial app with tools for tax calculations, invoicing, and compliance.
    \item Secured initial client engagements in legal and social enterprise sectors, delivering measurable improvements in reporting efficiency and operational clarity.
    \item Driving strategic growth roadmap: pricing models, data governance frameworks, and regional expansion.
\end{itemize}

\textbf{KCB Bank Kenya} — Nanyuki, KE \\
\textit{Personal Banker} \hfill Sep 2022 – Apr 2025
\begin{itemize}[leftmargin=*]
    \item Analysed customer transaction data and identified high value clients, increasing my sales conversion rates.
    \item Developed automated dashboards in Excel to track portfolio growth, improving the efficiency of lead targeting.
    \item Utilized SQL to extract insights from banking databases, supporting strategy in retail loan products.
\end{itemize}

\textbf{KCB Investment Bank} — Nairobi, KE \\
\textit{Trading Intern} \hfill Jul 2023 – Aug 2023
\begin{itemize}[leftmargin=*]
    \item Interned at the brokerage to learn various investment banking operations including compliance to NSE and CMA regulations, investor relations, and securities trading.
\end{itemize}

\section*{Projects}
\textbf{Fedha Tracker App} — Android (Java/Kotlin), Python, SQL, Google APIs, Git \\
\textit{Dec 2024 – Feb 2025}
\begin{itemize}[leftmargin=*]
    \item Designed and developed an Android-based financial tracker app for freelancers and SMEs with real-time expense tracking and financial optimization.
    \item Architected a mobile app with analytics for budgeting, report generation, and actionable insights.
    \item Implemented iterative development and user feedback integration.
    \item Built a scalable roadmap for a B2B SaaS platform.
\end{itemize}

\textbf{Predictive Analytics} — Python, Random Forests, R, R Studio, R Markdown \\
\textit{Mar – Oct 2023}
\begin{itemize}[leftmargin=*]
    \item Applied predictive analytics and ML (logistic regression, random forests) on ecommerce data to predict sales conversion.
    \item Integrated GitHub OAuth and visualized team collaboration data.
\end{itemize}

\textbf{OCR Extraction Tool} — Python, Tesseract OCR, pdf2image, OpenCV \\
\textit{Mar 2025 – Present}
\begin{itemize}[leftmargin=*]
    \item Built a tool to extract text from scanned documents including secure PDFs with tables.
    \item Created a reproducible Conda environment and automated reporting pipelines.
\end{itemize}

\section*{Technical Skills}
\textbf{Languages:} Python, C/C++, SQL (Postgres), JavaScript, HTML/CSS, R, Java \\
\textbf{Frameworks:} React, Flutter, Node.js, Flask, Material-UI, FastAPI, Django \\
\textbf{Developer Tools:} Git, Jupyter Notebooks, Docker, GCP, VS Code, PyCharm, IntelliJ, Eclipse \\
\textbf{Libraries:} pandas, NumPy, Matplotlib

\end{document}
